\section{Ethics and Values}

\subsection{Ethical Approach}
\subsection{Societal impact of our application}
\subsection{Possible outcomes resulting from our application}

\indent \indent Our full-stack web application uses two different types of translation services: Amazon Translate and our own transformer-based translation model trained on a data set consisting of manually translated Amazon Web Service blog posts. Due to our application relying heavily on machine learning models in order to translate blog posts from English to Turkish, there is room for ethical concern when working with these models. 

\indent The translations completed by our model are important to increase the accessibility of information to native Turkish speakers. Through the use of this service, these users should be able to access the same information as any other user that is proficient in a high-resource language. The quality of the translation that our model outputs has a high impact on the user's ability to understand the blogposts; a high-quality translation service will increase user satisfaction and experience by allowing more users access to significant technical information residing in the blog posts. In the case that we achieve a good translation model, more users will be reached through AWS markets which will have a mutually beneficial outcome for our client as well as AWS customers/users. However, in the case that we achieve a low-quality translation, these users will not be given access to important information that they should have. 

\indent Although we will be training our model on a manually translated data set, it is significant to consider the difficulties regarding translating English to Turkish since we may not be able to catch the accurate meaning of the sentences with the limited data set we have. Inaccurate translations have the potential to be harmful to users who wish to acquaint themselves with information regarding AWS in terms of time and cost (for example, our model could inaccurately translate the way an AWS service works, leading to time and possible money lost as the user who is reading the blog could carry this mistake over into their work). 

In general, we have found that our translation model does not pose much of a concern regarding human rights and values as our model is intended to only work with AWS blog posts that mostly remain technical and related to AWS Services, so there is little room for dangerous translations. Furthermore, since our application is very connected to user experience, before our finished product, we will do acceptance testing to ensure the quality of our translation as well as a good user experience. We will try to improve our translation by gathering more training data from other resources to strive for a high-quality translation service.  
